### 2023-10-02 vesicle_code/docs/confinedMulti/response.tex

\begin{enumerate}
%%%%%%%%
\item In the phase energy, Eq.~(5), it is stated that the parameter
  $\epsilon$ is much smaller than 1 but then it is stated that this
    parameter is equal to 100. Please address this inconsistency.

\noindent
{\bf Response:} This was our oversight. The parameter values for $a$ and
$\epsilon$ were unintentionally reversed. This has been fixed.

%%%%%%%%
\item What motivated the choice of a sigmoid function, Eq.~(9), rather
  than a simple min/max operation so that the bending rigidity does not
    extend past the $[0.1, 1]$ range? Would the use of a regular-mixture
    model, which might be more physically realistic, remove the need for
    such a mathematical approximation as the equilibrium concentrations
    will no longer be $0$ and $1$?

\noindent
{\bf Response:} Because we are using an integral equation formulation,
    we are able to achieve high-order accuracy as long as everything is
    smooth, including the vesicle shape, tension, and the bending
    stiffness. If we used any kind of $\max$ or $\min$ function, the
    bending modulus would lose differentiability and this would result
    in a loss of accuracy. We have expanded the text to explain this
    point.

    We are unsure what the reviewer means by a ``regular-mixture model".
    If they mean a linear parameterization between the stiff and floppy
    phases, this is exactly equation (8).  We originally used this
    choice, but as argued in the manuscript, because of the strong
    confinement, the lipid concentration could easily exceed a value of
    $1$, and this resulted in a unphysical negative bending stiffness
    which ultimately leads to an instability.  Figure 2 demonstrates
    this effect. Furthermore, Figure 3 validates the choice of the
    sigmoid parameterization by comparing the results with a result from
    the literature that used the linear parameterization in an unbounded
    linear shear flow.

@@

The referee wrote: The authors of the paper, explored the effect of
hydrodynamics on the behavior of multicomponent vesicles under strong
confinement using numerical simulations. They have elucidated the
effects of the lubrication layer that exists between the vesicle, and
explored how confinement affects the excess pressure needed to push the
vesicle through the conduit. This study is useful to the community and
contains some sound insights regarding multicomponent vesicles. It,
however, is important that the authors make the following changes to be
considered for publication.

\noindent
{\bf Response:}: We thank the referee for their assessment and suggested
changes.

\begin{enumerate}
%%%%%%%%
\item The authors specify a line energy parameter $\epsilon = 100$. It
  is important that the authors justify this choice along with an
    experimental study which uses similar parameter ranges. This is
    important so that a future experimental study could be performed
    using these parameters as a guide.

\noindent
{\bf Response:} This was our oversight. The parameter values for $a$ and
$\epsilon$ were unintentionally reversed. This has been fixed. TODO:
    Need to justify the actual values we used. Take a look at the series
    of Lowengrub/Shuwang papers.

@@

%%%%%%%%
\item The authors measure the tangential velocity at 4 points. They
  should provide some justification for this number. Also, it is
    advisable that in Figure 7, the authors use a different color for
    each velocity plot. The plot looks highly convoluted and does not
    convey the message clearly. Also, what are the bounds within which
    the authors call the tangential velocity to be constant in Figure 7?
    They should define a bound for the variation that could be
    considered constant. Moreover, in Figure 7, for the floppy vesicle,
    the authors see a large deviation for the tangential velocity. It
    doesn't seem like the velocity could be called `constant'. The
    authors should provide a more detailed explanation for this.

\noindent
{\bf Response:} A response

%%%%%%%%
\item In some simulations, the authors choose a `random' initial
  condition. It would be helpful if they could mathematically define the
    function for this initial condition.

\noindent {\bf Response:} The examples with a random initial condition
    use the uniform distribution with the range $[0,1]$ to define the
    concentration $u$ at each spatial point. Given the choices of
    $b_{\min}=0.1$ and $b_{\max}=1$, the resulting mean bending
    stiffness is $\overline{b(u)} \approx 0.55$. The text has been
    adjusted at the start of Section 3.1 and Section 3.2.

@@

%%%%%%%%
\item In Figure 6, the author should comment on the energy behavior of
  the floppy vesicle in the stenosis region.

\noindent
{\bf Response:} A comment has been included.

%%%%%%%%
\item In Figure 7, when the authors look at the excess pressure plots,
  they should describe the behavior of the floppy vesicle due to the
  difference in lubrication thickness and, in turn, excess pressure. It
  seems like the excess pressure shows a similar trend as the stiff
  vesicle.

\noindent
{\bf Response:} In the original submission, we attempted to relate the
excess pressure to the lubrication layer thickness. However, as pointed
out by the reviewer, we did not make any reference to the floppy case.
As a general trend, we find that the sum of the top and bottom
lubrication layer thicknesses is correlated with the magnitude of the
excess pressure---larger lubrication layers correspond to smaller (less
negative) excess pressures. This is because smaller excess pressure is
required to push the same amount of fluid around the vesicle when the
lubrication layer thickness is larger.

@@

\begin{enumerate}
%%%%%%%%
\item This study is limited to the two-dimensional case, which is not
  reality. It is a strong approximation and full 3D studies are still a
    challenge in constrictions. But, in the axisymmetrical case, there
    are several results in literature which could be more or less,
    considered as benchmark:
    \url{http://dx.doi.org/10.1103/PhysRevFluids.5.043602}, \\
    \url{https://doi.org/10.1017/jfm.2017.743}

\noindent
{\bf Response:} A response

%%%%%%%%
\item The authors should justify why they limit their investigations to
  the 2D case if 3D is possible. I note that the authors also cite
    relevant literature as 10, 11 $\ldots$ References to 2D are
    excellent. A typical argument is the high time of 3D simulations.
    Can the authors provide an order of magnitude?

\noindent
{\bf Response:} There are 3D BIE codes for vesicles with surface
    rheology. Leonetti did in 2016 in paper Yuan is sending me. There,
    of course, is also plenty of accurate methods for single-component
    vesicles in 3D with strong confinement. This will be even more
    challenging with strong confinement. Only methods in the literature
    seem to be David Salac which is a low-order method. Can reference
    private discussions Zhangli Peng at UIC.

    A response

@@

%%%%%%%%
\item The authors present the essential steps of the numerical model. It
  is well done and the references well chosen. I have appreciated the
    introduction of equation (9) an figure 2. However, there are two
    points to clarify :
    \begin{itemize}
      \item page 2 : there is a difference in literature of the
        capillary number. Some authors use the flow curvature, others
        the mean velocity as the authors. Please explain your choice.
      \item page 2, right column ``The parameter $\epsilon \ll 1$ sets
        the size of the transition region of u, and the parameter a is
        line tension scaled by the characteristic bending stiffness. All
        simulations use the parameter values $\epsilon = 100$ and $a =
        0.04.$" $\epsilon = 100$ is contradictory to $\epsilon \ll 1$.
        Please explain or correct
    \end{itemize}

\noindent
{\bf Response:} This was our oversight. The parameter values for $a$ and
$\epsilon$ were unintentionally reversed. This has been fixed.

%%%%%%%%
\item Why do authors never observe the blocking of vesicles contrary to
  experiments? It would the opportunity to perform a phase diagram and
    to show the effect of multicomponent.

\noindent
{\bf Response:} FIRST ROUGH DRAFT: We did observe cases where
    multicomponent vesicles are stuck. However, keeping all other
    parameters fixed, the corresponding single-component vesicles were
    also stuck. We were hoping to find cases where the multicomponent
    vesicle passed through the contracting geometry while the
    single-component vesicles did not (similar to our semipermeable
    work), but no such case was found.  For this reason, we have focused
    on the effect that multicomponent has on the vesicle shape, tension,
    layer thickness, tank treading, etc.

@@

%%%%%%%%
\item In experiments, the channel is a slit. What do the authors expect
  from such a difference?

\noindent
{\bf Response:} We can compare Zhangli Peng's results, our simulations
look similar to what they observe in a 2D projection of their 3D
results. They call their geometry a `slit' geometry. This work is
published, so we can reference a particular figure from the paper.

### 2023-10-02 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic since $b(u) < 0$ if $u > (1 - \beta)^{-1}$,
and such values of $u$ are possible when $\beta \ll 1$, $Ca \gg 1$, or
the vesicle is confined to a narrow region. This behavior is
demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
floppy-to-stiff ratio $\beta = 10^{-1}$ entering a stenosis. Using the
linear bending model in Equation~\eqref{eqn:linearBending}, the lipid
concentration achieves a maximum value of $u \approx 1.5$ which results
in an instability that is formed by the resulting unphysical negative
bending stiffness. To rectify this issue, we parameterize the bending
modulus with the sigmoid function
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, $b(u)$ remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). We compare this new bending model against the linear model for 
a phase-treading and tank treading vesicle in Section~\ref{sec:validation}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:NumericalMethods}Numerical Methods}
We use a high-order integral equation formulation to resolve the complex
vesicle shapes and long-range hydrodynamic interactions. The velocity
field $\uu$ at $\xx \in \Omega$ is written as a combination of a
single-layer potential and a double-layer potential
\begin{align}
  \label{eqn:LPrep}
  \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
  S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} 
      \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
$\rr = \xx - \yy$, $\rho = |\rr|$,
\textcolor{blue}{
$\nn$ is the outward unit normal, $\eeta$ is a currently unknown density
function,}
and $\mathds{I}$ is the $2 \times 2$ identity matrix. 
\textcolor{blue}{
The membrane tension $\sigma$ acts as a Lagrange multiplier so that the
inextensibility condition, $\nabla_{\gamma} \cdot \uu = 0$, can be
satisfied.}
The corresponding pressure is
\begin{align}
  \label{eqn:pressure}
  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
    \nn \cdot \eeta \, ds_\yy.
\end{align}

To avoid tangling, the vesicle membrane is parameterized in terms of the
$\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed
vesicle length and $\theta$ is the angle between the tangent vector and
the positive $x$-axis. This requires decomposing the velocity field on
$\gamma$ into a normal velocity $V$ and tangential velocity $T$. Then,
the no-slip boundary condition for the vesicle velocity is
\begin{align}
  \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is satisfied by requiring that
$\eeta$ satisfies
\begin{align}
  \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma,
  \label{eqn:DLP_BIE}
\end{align}
\textcolor{blue}{
where the fluid velocity on the solid wall is defined in
Equation~\eqref{eqn:dirBC}.}

@@

\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
  \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
  single-component; (b) floppy single-component; (c) multicomponent.
  \textcolor{blue}{The background flow is in the positive $x$ direction
  denoted by the arrow.}}
\end{figure*}

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$. With the
current setup and $Ca=0.25$, an elliptical vesicle with reduced area
greater than $\alpha = 0.8$ cannot fit through the closely-fitting
geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. 
\textcolor{blue}{
The lipid distribution at each point on the multicomponent vesicle is
chosen randomly from the uniform distribution with the range $[0,1]$. As
a result of selecting $b_{\min}=0.1$ and $b_{\max}=1$, the mean bending
stiffness is $\overline{b(u)} = 0.55$.}
%The lipid distribution of the multicomponent vesicle is
%initially random with a mean value of 0.55. 
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new sigmoid bending modulus in Equation~\eqref{eqn:tanhBending}. A
single Lagrangian point is included to visualize any tank-treading
behavior. There are slight differences between the three cases, with the
most noticeable being that the multicomponent vesicle has higher
curvature in the floppy region. However, in general, there is little
difference between these cases, principally because these vesicles have
a large reduced area.

\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
  \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
  single-component; (b) floppy single-component; (c) multicomponent.
  \textcolor{blue}{The background flow is in the positive $x$ direction
  denoted by the arrow.}}
\end{figure*}

@@

We next consider a vesicle with a smaller reduced area $\alpha=0.4$ with
the same geometry and capillary number. Figure~\ref{fig:RA4} shows the
shape of a (a) stiff single-component, (b) floppy single-component, and
(c) multicomponent vesicle at six locations along the stenosis channel.
Contrary to the vesicles with the larger reduced area
(Figure~\ref{fig:RA6}), the bending modulus has a large effect on the
vesicle shape. We first consider the three different energies---bending,
tension, and phase---for each example. In Figure~\ref{fig:Energy}, we
plot these energies as a function of the vesicle's center. Note that the
single-component vesicles do not have a phase energy. We observe that,
as the vesicle enters the stenosis, it develops regions of high
curvature, and this results in an increase in the bending energy. As
the stiff single-component and multicomponent vesicles reach a
steady-state shape near the middle of the channel, their bending and
tension energies remain nearly constant from $x=0$ until the end of the
stenosis. 
\textcolor{blue}{
In contrast, the bending and tension energies of the floppy
single-component vesicle evolve throughout the entire channel as the
vesicle undergoes deformations.}
For the multicomponent vesicle, the phase energy is also nearly constant
in this region. This implies that there is no coarsening of lipid phase
parameter in the middle of a stenosis.

@@

The sizes of the top and bottom lubrication layers are also related to
the excess pressure. The green curve on the top half of
Figure~\ref{fig:lubricationComposite} shows the excess pressure (with
the axis aligned on the right side of the plot). 
\textcolor{blue}{
As a general trend, we expect that if the total lubrication layer
thickness---namely the sum of the top and bottom lubrication layers---is
largest, then less pressure is required to maintain the constant flow
rate, and the result is a smaller (less negative) excess pressure. This
trend is confirmed in Figure~\ref{fig:lubricationComposite} where the
size of the lubrication layers, from smallest to largest, are the stiff
single-component vesicle, the floppy single-component vesicle, and the
multicomponent vesicle, while the ranking of the excess pressure is
reversed.}
%When the lubrication layers are large, most notably for the
%multicomponent vesicle, less pressure is required to force the vesicle
%through the geometry, and the result is a smaller (less negative)
%excess pressure. In contrast, when the lubrication layers are small,
%most notably for the stiff single-component vesicle, more pressure is
%required to force the vesicle through the geometry, and we the result
%is a larger (more negative) excess pressure.

>>>>

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic since $b(u) < 0$ if $u > (1 - \beta)^{-1}$,
and such values of $u$ are possible when $\beta \ll 1$, $Ca \gg 1$, or
the vesicle is confined to a narrow region. This behavior is
demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
floppy-to-stiff ratio $\beta = 10^{-1}$ entering a stenosis. Using the
linear bending model in Equation~\eqref{eqn:linearBending}, the lipid
concentration achieves a maximum value of $u \approx 1.5$ which results
in an instability that is formed by the resulting unphysical negative
bending stiffness. 
\textcolor{blue}{
To rectify this issue, we could simply restrict the bending modulus to
be bounded in $[b_{\min},b_{\max}]$ by letting $b(u) = \max\left( \min
\left( (1-u) + \beta u,1 \right), \beta \right)$. However, the loss of
differentiability would result in a loss of accuracy.
}
Instead, we parameterize the bending modulus with the sigmoid function
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, $b(u)$ remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). We compare this new bending model
against the linear model for a phase-treading and tank treading vesicle
in Section~\ref{sec:validation}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:NumericalMethods}Numerical Methods}
We use a high-order integral equation formulation to resolve the complex
vesicle shapes and long-range hydrodynamic interactions. The velocity
field $\uu$ at $\xx \in \Omega$ is written as a combination of a
single-layer potential and a double-layer potential
\begin{align}
  \label{eqn:LPrep}
  \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
  S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} 
      \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
$\rr = \xx - \yy$, $\rho = |\rr|$,
\textcolor{blue}{
$\nn$ is the outward unit normal, $\eeta$ is a stress density,}
and $\mathds{I}$ is the $2 \times 2$ identity matrix. 
\textcolor{blue}{
The membrane tension $\sigma$ acts as a Lagrange multiplier so that the
inextensibility condition, $\nabla_{\gamma} \cdot \uu = 0$, can be
satisfied.}
The corresponding pressure is
\begin{align}
  \label{eqn:pressure}
  p(\xx) = \frac{1}{2\pi} \int_{\gamma} \frac{\rr \cdot \ff}{\rho^2} \, ds_\yy + 
    \frac{1}{\pi} \int_{\Gamma} \frac{1}{\rho^2} 
    \left(\mathds{I} - 2\frac{\rr \otimes \rr}{\rho^2} \right) 
    \nn \cdot \eeta \, ds_\yy.
\end{align}

To avoid tangling, the vesicle membrane is parameterized in terms of the
$\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed
vesicle length and $\theta$ is the angle between the tangent vector and
the positive $x$-axis. This requires decomposing the velocity field on
$\gamma$ into a normal velocity $V$ and tangential velocity $T$. Then,
the no-slip boundary condition for the vesicle velocity is
\begin{align}
  \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is satisfied by requiring that
$\eeta$ satisfies
\begin{align}
  \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma,
  \label{eqn:DLP_BIE}
\end{align}
\textcolor{blue}{
where the fluid velocity $\UU$ on the solid wall $\Gamma$ is defined in
Equation~\eqref{eqn:dirBC}.}

@@

\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp6MCp5.pdf}
  \caption{\label{fig:RA6} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.6$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
  single-component; (b) floppy single-component; (c) multicomponent.
  \textcolor{blue}{The imposed flow is in the positive $x$ direction
  denoted by the arrow.}}
\end{figure*}

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$. With the
current setup and $Ca=0.25$, an elliptical vesicle with reduced area
greater than $\alpha = 0.8$ cannot fit through the closely-fitting
geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. 
\textcolor{blue}{
The lipid distribution at each point on the multicomponent vesicle is
chosen randomly from the uniform distribution with the range $[0,1]$.
Since $b_{\min}=0.1$ and $b_{\max}=1$, the mean bending stiffness is
$\overline{b(u)} \approx 0.55$.}
%The lipid distribution of the multicomponent vesicle is
%initially random with a mean value of 0.55. 
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new sigmoid bending modulus in Equation~\eqref{eqn:tanhBending}. A
single Lagrangian point is included to visualize any tank-treading
behavior. There are slight differences between the three cases, with the
most noticeable being that the multicomponent vesicle has higher
curvature in the floppy region. However, in general, there is little
difference between these cases, principally because these vesicles have
a large reduced area.

\begin{figure*}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/STENOSIS_RAp4MCp5.pdf}
  \caption{\label{fig:RA4} \small A vesicle passing through the stenosis
  geometry. The vesicle's reduced area is $\alpha = 0.4$ and the
  capillary number is $Ca = 0.25$. The vesicles are: (a) stiff
  single-component; (b) floppy single-component; (c) multicomponent.
  \textcolor{blue}{The imposed flow is in the positive $x$ direction
  denoted by the arrow.}}
\end{figure*}

@@

We next consider a vesicle with a smaller reduced area $\alpha=0.4$ with
the same geometry and capillary number. Figure~\ref{fig:RA4} shows the
shape of a (a) stiff single-component, (b) floppy single-component, and
(c) multicomponent vesicle at six locations along the stenosis channel.
Contrary to the vesicles with the larger reduced area
(Figure~\ref{fig:RA6}), the bending modulus has a large effect on the
vesicle shape. We first consider the three different energies---bending,
tension, and phase---for each example. In Figure~\ref{fig:Energy}, we
plot these energies as a function of the vesicle's center. Note that the
single-component vesicles do not have a phase energy. We observe that,
as the vesicle enters the stenosis, it develops regions of high
curvature, and this results in an increase in the bending energy. As
the stiff single-component and multicomponent vesicles reach a
steady-state shape near the middle of the channel, their bending and
tension energies remain nearly constant from $x=0$ until the end of the
stenosis. 
\textcolor{blue}{
For the floppy case, the bending energy is similar in size as the stiff
case. Since the floppy bending modulus is ten-times smaller than the
stiff case, this indicates that the curvature of the floppy vesicle is
about $\sqrt{10}$-times larger than the stiff case. This additional
curvature corresponds to larger and more dynamic membrane deformations,
and a more varying tension energy.}
For the multicomponent vesicle, the phase energy is also nearly constant
in this region. This implies that there is no coarsening of lipid phase
parameter in the middle of a stenosis.

@@

The sizes of the top and bottom lubrication layers are also related to
the excess pressure. The green curve on the top half of
Figure~\ref{fig:lubricationComposite} shows the excess pressure (with
the axis aligned on the right side of the plot). 
\textcolor{blue}{
As a general trend, we find that the sum of the top and bottom
lubrication layer thicknesses is correlated with the magnitude of the
excess pressure---larger lubrication layers correspond to smaller (less
negative) excess pressures. This is because smaller excess pressure is
required to push the same amount of fluid around the vesicle when the
lubrication layer thickness is larger.}
%As a general trend, we expect that if the total lubrication layer
%thickness---namely the sum of the top and bottom lubrication layers---is
%largest, then less pressure is required to maintain the constant flow
%rate, and the result is a smaller (less negative) excess pressure. This
%trend is confirmed in Figure~\ref{fig:lubricationComposite} where the
%size of the lubrication layers, from smallest to largest, are the stiff
%single-component vesicle, the floppy single-component vesicle, and the
%multicomponent vesicle, while the ranking of the excess pressure is
%reversed.}
%When the lubrication layers are large, most notably for the
%multicomponent vesicle, less pressure is required to force the vesicle
%through the geometry, and the result is a smaller (less negative)
%excess pressure. In contrast, when the lubrication layers are small,
%most notably for the stiff single-component vesicle, more pressure is
%required to force the vesicle through the geometry, and we the result
%is a larger (more negative) excess pressure.
